%% Margins
\voffset=-10.4mm
\hoffset=-10.4mm

\vsize=267mm
\hsize=180mm
\parindent=0pt

%% Font Aliases
\font\title = "Optima/B:Letter Case=Small Caps" at 24pt
\font\main = "Optima" at 11pt
\font\bf   = "Optima/B" at 11pt
\font\it   = "Optima/I" at 11pt
\font\sc = "Optima" at 12pt
\font\tt = "Monaco" at 9pt 
\font\tinyrm = "Optima" at 7pt
\font\lllsize = "Optima" at 8pt
\font\smallit = "Optima/I" at 8pt 


%% Predefined strings
\def\plus{\raise .5ex \hbox{\tinyrm +}}
\def\plusplus{\raise .5ex \hbox{\tinyrm ++}}
\def\LaTeX{%
  L\kern-.36em           
  {\setbox0=\hbox{T}%
   \vbox to \ht0{\hbox{\lllsize A}\vss}}%
  \kern-.15em
  \TeX
}

%% Commands for organistion
\def\cvsection#1{{\sc #1} \smallskip \hrule \medskip}
\def\jobheader#1#2#3#4{\line{{\bf #1} \hfill #2}\line{#3 \hfill #4}}

%% Don't hyphenate these words
\hyphenation{OpenSolaris}

%% Name
\def\author{R Thomas Harper}

%%%%% START OF DOCUMENT %%%%% 
\main
\footline{\it \author\ — Curriculum Vitæ \hfill Page \the\pageno}

{\title \author}
\hrule %%height 1 pt

\smallskip
d
%% Contact Info
\line{L \hfill +46 70-001 27 26}
\line{113 59 Stockholm \hfill rtomharper@gmail.com}
\line{Sweden           \hfill}

\bigskip

%% Education
\cvsection{Education}
\line{{\bf Doctor of Philosophy in Computer Science} \hfill Currently pursuing}
\line{Oriel College, University of Oxford, Oxford, United Kingdom \hfill}
\line{Supervised by Dr Ralf Hinze \hfill}
\medskip
\line{{\bf Master of Science in Computer Science} \hfill 2008}
\line{St Anne's College, University of Oxford, Oxford, United Kingdom \hfill}
\line{Dissertation: {\it Fusion on Haskell Unicode Strings} \hfill}
\line{Supervised by Prof Oege de Moor \hfill}
\medskip
\line{{\bf Bachelor of Science {\it cum laude} in Computer Science}
  \hfill 2004–2007}
\line{Syracuse University, Syracuse, New York, United States\hfill}

\bigskip

%% Awards and Honours 
\cvsection{Awards and Honours} 

\line{National Society of Collegiate Scholars \hfill 2006}
\line{Dean's Scholarship — Syracuse University \hfill 2004}
\line{President's Scholarship — American University \hfill 2003}

\bigskip

%% Teaching Experience
\cvsection{Teaching Experience}

\jobheader{Demonstrator}{2008–Present}{Oxford University
Computing Laboratory}{Oxford, United Kingdom}
\smallskip

\parindent=20pt
\item{$\diamond$} Instruct undergraduate and graduate students in the
concepts necessary to complete practical exercises.
\item{$\diamond$} Provide one-on-one assistance to students as they
complete practicals in a lab.
\item{$\diamond$} Mark completed assignments and give feedback to students.
\item{$\diamond$} Assist at Open Days and Access Days demonstrating
the pedagogical language GeomLab.
\parindent=0pt

\smallskip

\parindent=20pt
\indent Courses Taught:
\parindent=40pt
\item{$\diamond$} Functional Programming
\item{$\diamond$} Computational Linguistics
\item{$\diamond$} Compilers
\item{$\diamond$} Principles of Programming Languages
\parindent=0pt

\bigskip

%% Research Interests
\cvsection{Research Interests}

My research focuses on functional programming.  I am interested in the
design of functional algorithms and purely functional data structures.
For my thesis, I am studying the use of fusion techniques to automatically
remove intermediate data structures from recursive programs.  

\bigskip

\cvsection{Research Experience}

\jobheader{Doctoral Research}{2008–Present}
{Oxford University Computing Laboratory}{Oxford, United Kingdom}
\medskip

\parindent=20pt
\item{$\diamond$} Conduct research into using fusion as a program
optimisation in functional programming languages. 
\item{$\diamond$} Design and implement purely functional data
structures in the Haskell programming language and adapt fusion
techniques for them. 
\item{$\diamond$} Use high level equational reasoning
and core output from a compiler to evaluate lower-level implications of
optimisation. 
\item{$\diamond$} Develop benchmarking techniques to evaluate the efficacy of
optimisations.
\item{$\diamond$} Collaborate on papers relevant to this research.
\item{$\diamond$} Present and publish results at relevant international conferences.
\parindent=0pt

\bigskip

\jobheader{Master's Research}{2007–2008}
{Oxford University Computing Laboratory}{Oxford, United Kingdom}
\medskip

\parindent=20pt
\item{$\diamond$} Designed and implemented a high-performance, unicode
compliant string library
in the Haskell programming language using a novel application of
stream fusion.
\item{$\diamond$} Examined GHC core language output to find and optimise
low-level inefficiences.
\item{$\diamond$} Created a functional, high-level interface for
efficient code that exploited low-level data manipulation to achieve
good performance.
\item{$\diamond$} Demonstrated performance improvements quantitatively using benchmarks.
\item{$\diamond$} Presented the results in a dissertation which earned a Distinction-level mark.
\item{$\diamond$} Published the results and presented them at
Implementation and Application of Functional Languages (IFL) 2009.

\bigskip

\jobheader{Research Aid}{June 2006–August 2006}
{Air Force Research Lab/Rome Research Site}{Rome, New York, United States}
\medskip

\parindent=20pt
\item{$\diamond$} Conducted machine translation research for the
Information Exploitation division.
\item{$\diamond$} Evaluated research from a contracted company on
statistical machine translation and documented the results. 
\item{$\diamond$} Extended that research
by creating an integrated statistical machine translation application
with a graphical user interface. This application was
proof-of-concept code for use in constructing similar products for
government and military customers. 
\item{$\diamond$} Helped organise the “Military and Security
Applications of Evolutionary Computing” workshop for the Genetic and
Evolutionary Computing Conference (GECCO) 2006.
\parindent=0pt

\bigskip

%% Professional Experience
\cvsection{Professional Experience}

\jobheader{Summer of Code Participant}{June 2007–August 2007}{Google, Inc.}{}
\medskip 

\parindent=20pt
\item{$\diamond$} Submitted a proposal titled “Porting Fast Fourier
Transform Tools” which was accepted by the OpenSolaris project. 
\item{$\diamond$} Under the supervision of a mentor from Sun Microsystems,
Inc., optimised Mlucas, a Lucas-Lehmer primality
tester. 
\item{$\diamond$} Parallelised source code using OpenMP, achieving a high degree
of speedup on Sun servers.  
\item{$\diamond$} This became the most scalable Mersenne
Prime verifier used by the Great Internet Mersenne Prime Search.
\parindent=0pt

\bigskip

\jobheader{Information Systems Intern}{June 2005–September
2005}{Anheuser-Busch, Inc.}{Baldwinsville, New York, United States}
\medskip

\parindent=20pt
\item{$\diamond$} Supported a 24/7/365 brewery as a member of the
Information Systems department.  
\item{$\diamond$} Provided end-user support for software, hardware, and
network issues in production and office environments.  
\item{$\diamond$} Performed maintenance on live process control systems. 
\item{$\diamond$} Performed routine system maintenance on servers.  
\item{$\diamond$} Assisted in a plant-wide upgrade of
over 500 computers using remote administration and by managing
contracted workers for hardware replacement.
\parindent=0pt

\bigskip

%% Skills
\cvsection{Skills} 

{\bf Programming Languages} 

Haskell, $x$86, Assembly, C, C\plusplus, C$\sharp$, Java,
Lua, OCaml, Perl, Scala
\parindent=0pt
\medskip

% {\bf System Software}

% Fedora, FreeBSD, Mac OS X, MS-DOS, Microsoft Windows 9$x$, NT, ME,
% 2000 (incl. Server), and XP, Sun Solaris, OpenMP, Qt, Visual C$\sharp$
% \medskip

% {\bf Professional Software}

% Adobe Creative Suite, \LaTeX, Microsoft Office, Plain
% \TeX, QuickBooks, R \medskip

{\bf Languages}

Native English, Fluent Spanish, Intermediate Icelandic, Irish and
Welsh

\bigskip

%% References

\cvsection{References}

The following persons have submitted letters of references on my
behalf:

\smallskip

\settabs 2 \columns
\+ Ralf Hinze                         & Irina Voiculescu                        \cr
\+ Reader                             & Departmental Lecturer                   \cr
\+ Oxford Computing Laboratory        & Oxford Computing Laboratory             \cr
\+ Wolfson Building                   & Wolfson Building                        \cr
\+ Parks Road                         & Parks Road                              \cr
\+ Oxford                             & Oxford                                  \cr
\+ OX1 3QD                            & OX1 3QD                                 \cr
\+ +44 (0)1865 610 700                & +44 (0)1865 283 501                     \cr
\+ ralf.hinze@comlab.ox.ac.uk         & irina.voiculescu@comlab.ox.ac.uk        \cr

\bigskip

%% Grants Awarded

%% Publications

\cvsection{Publications}

\hangindent=20pt
Harper, Thomas. Stream fusion on Haskell Unicode strings. In {\it
Implementation and Application of Functional Languages},
2009. Springer-Verlag. To appear.

%% Conference Presentations

%% Professional Activities

%% Professional Affiliations

%% Teaching Interests

\bye
